% !TeX program = xelatex

\documentclass[]{plushcv}

\begin{document}
\thispagestyle{empty}
% TITLE
\namesection{Daniil}{Aktanka}{Sustainable Systems Engineer}{
	\contactline{
		\href{https://www.linkedin.com/in/daniil-aktanka/}{daniil-aktanka}}
		{\href{https://www.github.com/akthonka}{akthonka}}
		{daniil\_aktanka@proton.me}
		{‎‪+41\,(0)798266155}
		}

%\vspace*{1cm}
%  LEFT COLUMN ______________________________________
\begin{minipage}[t]{0.70\textwidth} 

\section{Personal Statement}
{\justifying As an experienced engineer with a background in data science and sustainability, I am currently advancing my expertise in project management, business strategy, and risk engineering at UCL. This degree marks a strategic pivot in my career, bridging my technical acumen with managerial insights.}



% Experience
\section{Experience}
	\runsubsection{STM Minerals AG}
	\descript{\underline{Technical Assistance Engineer}}
	\location{Aug 2020 - Jul 2023 | Baden, CH}
	\vspace{\topsep} % Hacky fix for awkward vertical space
	\begin{tightemize}
		\item Directed initiation, planning and execution project phases of an industrial-grade IoT hardware product and cloud service for both internal and external use. Spearheaded system engineering design as well as programming development. Launched a new, internal, company database.
%		\paragraph{Specifics:}\vspace*{-12pt}
%		The product enables remote PLC data readout (Allen-Bradley \& Siemens), local-hardware backup \& sync and server data collection (MariaDB). The system supports integration with realtime cloud-based dashboard visualization and data processing (Grafana).
		\item Created and maintained a MATLAB App Designer software tool (3k+ lines) for company mill-sizing purposes. The tool features multiple internal data-structures, dynamic UI elements and elaborate plot visualizations with built-in data model extrapolations. Approved for use by both sales and engineering departments.
		\item Assessed and systematized methodology for grinding-media filling-level computation. Proposed additional uncertainty correction methods to account for slurry density variation using 3D linear data extrapolation. Collaborated on industrial product design solution.
	\end{tightemize}
	\subskip
	
	\runsubsection{STM Minerals AG}
	\descript{\underline{Engineer Intern}}
	\location{Aug 2019 - Jul 2020 | Baden, CH}
	\begin{tightemize}
		\item Investigated temporal relationship between strain-gauge voltage and grinding-media filling-level. Performed data cleaning and analysis in python via pandas and XGBoost machine learning.
		\item Designed and developed a VBA UserForm script (1k+ lines) for efficient document parsing and automation. Simplified commissioning engineers' workflow and improved team's performance by reducing test-report document processing time by $\approx$83\% per project. 
		\item Consulted in electrical-engineering document standardization. Designed and created standardized templates for piping and instrumentation diagrams.
	\end{tightemize}



% Projects
\section{Projects}
	\runsubsection{Job Application Autofiller}
	\descript{2023 | Python (selenium), JavaScript}
	\begin{tightemize}
		\item A tool designed to navigate and fill common webpage form fields, with GUI. Accounts for naming variability using an internal database with regex parsing.
	\end{tightemize}
	\sectionsep

	\runsubsection{Power flow simulation analysis}
	\descript{2023 | Python (pandas, pandapower)}
	\begin{tightemize}
	\item "Electric Vehicles in Energy Communities: Investigating the Distribution Grid Hosting Capacity (BSc SSE thesis)".	Proposed a semi-coordinated energy-community EV charging pattern with a 30\% improvement of grid stability for low-voltage European grids, based on historical data.
	\end{tightemize}





% RIGHT COLUMN______________________________________

\end{minipage} \hfill
\begin{minipage}[t]{0.25\textwidth} 


\section{Education} 
	\subsection{MSc Technology\\ Management}
	\location{Sep 2023 - 2024}
	\descript{University College London}
	\sectionsep
	
	\subsection{Management\\ Essentials Course}
	\location{Jul 2022}
	\descript{Harvard Business School online}
	\sectionsep

	\subsection{BSc Sustainable\\Systems Engineering}
	\location{Sep 2020 - 2023}
	\descript{University of Freiburg}
	\sectionsep

%\vspace*{1cm}
\section{Skills}
	\subsection{Programming}
	\location{Experienced:}
	Python  \tb MATLAB \tb \LaTeX
	\subskip
	
	\location{Familiar:}
	SQL \tb JS \tb VBA \tb C \tb git 
	\sectionsep
	
	\subsection{Software}
	\location{Profficient:}
	Microsoft Office \tb Visio \tb Adobe Photoshop/Lightroom
	\sectionsep
	
	\subsection{Languages}
	\location{Native/C1 diploma:}
	English \tb Russian \tb German
	\subskip
	
	\location{Confident/B2.1 level:}
	French
	\sectionsep


\section{Interests}
	\subsection{Hobbies}
	\href{https://daniilaktanka.myportfolio.com/}{Photography} \tb Art

\end{minipage} 
\end{document}

